---
title: "Volaris"
author: "Jalil VOLARIS"
format: html
editor: visual
---

## Libraries

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
```

### Question 1

```{r}
here::i_am("eval-grades.Rproj")
library(here)
library(vroom)
grades <- vroom("grades.csv")
```

## Simple analyses

### Question 2

```{r}
nrow(grades)
```

The dataset contains 49422 grades.

### Question 3

```{r}
grades |>
  distinct(id) |>
  nrow()
```
The dataset includes 784 distinct students.

### Question 4

```{r}
students <- grades |>
  distinct(id, .keep_all = TRUE) |>
  select(id, group)
students |> slice_tail(n=5)
```

### Question 5

```{r}
ggplot(students, aes(x=group))+
  geom_bar()
```

### Question 6

```{r}
grades |>
  filter(course=="Martial Arts and Self-Defense") |>
  group_by(group) |>
  summarize(mean_maasd = mean(grade))
```

### Question 7

```{r}
ggplot(grades, aes(x=grade))+
  geom_density()+
  facet_wrap(vars(semester))
```

## Attendance analysis

### Question 8

```{r}
student_grades_count <- grades |>
  group_by(id, group) |>
  summarize(num_grades = n(), .groups = "drop")
head(student_grades_count)
```

```{r}
student_grades_count |>
  summarise(min = min(num_grades),
            max = max(num_grades),
            avg = mean(num_grades),
            med = median(num_grades))
```

### Question 9

```{r}
historyindia_grades <- grades |>
  filter(course == "History and Civilization of India") |>
  group_by(id, group) |>
  summarize(num_grades = n(), .groups = "drop")
head(historyindia_grades)
```

### Question 10

```{r}
ggplot(historyindia_grades, aes(x=num_grades))+
  geom_bar()
```

### Question 11

```{r}
ggplot(historyindia_grades, aes(x=num_grades))+
  geom_bar()+
  facet_wrap(vars(group))
```
It seems that all groups has roughly the same distribution.

## Grade analysis

### Question 12

```{r}
students <- grades |>
  group_by(id, course, group) |>
  summarise(mean = mean(grade))
students
```

```{r}
students_wider <- students |>
  pivot_wider(names_from=course,
              values_from=mean)
head(students_wider)
```
### Question 13

```{r}
ggplot(students_wider, aes(x=`Sanskrit Language and Literature`, y=`Vedic Philosophy and Spirituality`))+
  geom_point(alpha=0.5)
```

### Question 14

```{r}
students_wider |>
  group_by(group) |>
summarize(correlation = cor(`Sanskrit Language and Literature`, `Astrology and Astrology`, use = "complete.obs"))
```

### Question 15

```{r}
ggplot(students_wider, aes(x=`Astrology and Astrology`, y=`Sanskrit Language and Literature`))+
  geom_point()+
  facet_wrap(vars(group=1|2))
```

### Question 16

```{r}
final_average <- students_wider |>
  group_by(id, group) |>
  summarise(final_grade=mean(`Architecture and Sculpture`:`Yoga and Meditation`))|>
  arrange(-final_grade)
head(final_average)
```
### Question 17

```{r}
ggplot(final_average, aes(x=final_grade))+
  geom_density()+
  facet_wrap(vars(group))
```

### Question 18

### Question 19

### Question 20

